Preparación de datos

### 2022-05-25 production/prod_analysis.Rmd
base long full y restringida

```{r tab-desc, results="asis", warning=FALSE}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               car,         # recodificar variables
               sjlabelled,  # etiquetado de variables
               sjmisc,      # descriptivos y frecuencias
               sjPlot,      # tablas, plots y descriptivos
               knitr,
               kableExtra,
               summarytools,
               lavaan
               )
load(file = here::here("input/data-proc/study_1.RData"))

@@

# Df variables nivel 1
df<- dfSummary(df_study1 %>% select(in_simpat:edad),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               col.widths = c(700,10,10,10,10)
               )
df$Variable <- NULL # delete variable column
view(df,
     file = here::here("output/tables/desc01.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc01.html"),
        file =here::here("output/tables/desc01.png")) # Remover archivo HTML
print(df, method = "render")
```

>>>>

```{r tab-desc, results="asis", warning=FALSE}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools
               )
load(file = here::here("input/data-proc/df_study1_long.RData"))
load(file = here::here("input/data-proc/df_study1_long_t5.RData"))

@@

# Df variables nivel 1
df<- dfSummary(df_study1_long %>% select(in_simpat:edad),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               col.widths = c(700,10,10,10,10)
               )
df$Variable <- NULL # delete variable column
view(df,
     file = here::here("output/tables/desc01.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc01.html"),
        file =here::here("output/tables/desc01.png")) # Remover archivo HTML
print(df, method = "render")

# Df variables nivel __________________________________________________________
df<- dfSummary(df_study1_long_t5 %>% select(in_simpat:edad),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               col.widths = c(700,10,10,10,10)
               )
df$Variable <- NULL # delete variable column
view(df,
     file = here::here("output/tables/desc02.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc02.html"),
        file =here::here("output/tables/desc02.png")) # Remover archivo HTML
print(df, method = "render")
```

```{r}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4
               )
load(file = here::here("input/data-proc/df_study1_long.RData"))
load(file = here::here("input/data-proc/df_study1_long_t5.RData"))
```

### 2022-05-25 production/prod_prep.Rmd
base long full y restringida

#Recoding of education to years based on casen 2017.
elsoc_long_2016_2021$educ_n<- as.numeric(
  car::recode(elsoc_long_2016_2021$m01, 
              "1=0;2=4.3;3=7.5;4=9.8;5=12.02;6=13.9;
               7=14.8;8=14.9;9=16.9;10=19.07;c(-888,-999)=NA", 
              as.numeric = T))

elsoc_long_2016_2021$educ_n <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$educ_n,
                      label = "Education in years")

class(elsoc_long_2016_2021$educ_n)
sjmisc::frq(elsoc_long_2016_2021$educ_n)

@@

elsoc_long_2016_2021$nation <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$nation, 
                      label = "Nationality") 
elsoc_long_2016_2021$nation <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$nation,
                       labels = c("Chilean","Peruvian","Argentina","Colombian",
                                  "Bolivian", "Haitian","Spanish","Other"))
sjmisc::frq(elsoc_long_2016_2021$nation)

@@

@@

table(elsoc$nation==elsoc$nation_t1)
sjmisc::frq(elsoc$nation_t1)
elsoc$nation <- NULL; elsoc$nation_fix <- NULL; elsoc$check_nation <- NULL

elsoc$nation_t1 <- set_label(elsoc$nation_t1, label = "Nationality")

# KNOW inmigrants _____________________________
sjPlot::tab_xtab(elsoc$know_inm,
                 elsoc$ola,show.cell.prc = T,show.na = T)
sjmisc::frq(elsoc$know_inm)
elsoc$know_inm_bi <- car::recode(elsoc$know_inm,
                                                "1=0;2:5=1")
sjmisc::frq(elsoc$know_inm_bi)

know_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(
            know_inm_t1t4 = know_inm_bi[ola==4] - know_inm_bi[ola==1]
            )

elsoc <- left_join(x = elsoc,y = know_inm_bi, by = "idencuesta")
elsoc$know_inm_t1t4 <- set_label(elsoc$know_inm_t1t4,
                                  label = "Know immigrants (diff. t4 - t1)")
# sjmisc::frq(elsoc$know_inm_t1t4)
# sjPlot::tab_xtab(elsoc$know_inm_t1t4,elsoc$ola)

@@

frien_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(
            frien_inm_t1t4 = frien_inm_bi[ola==4] - frien_inm_bi[ola==1]
            )

elsoc <- left_join(x = elsoc,y = frien_inm_bi, by = "idencuesta")

elsoc$frien_inm_t1t4 <- set_label(elsoc$frien_inm_t1t4,
                                  label = "Have immigrant friends (diff. t4 - t1)")
# sjmisc::frq(elsoc$frien_inm_bi)
# sjmisc::frq(elsoc$frien_inm_t1t4)
# sjPlot::tab_xtab(elsoc$frien_inm_t1t4,elsoc$ola)

@@

df_study1 <- 
elsoc_long_2016_2021 %>% 
  select(idencuesta,ola,region,region_cod,comuna,comuna_cod,
         muestra,
         cuestion_mig,
         starts_with("in_"),
         educ,educ_n,ing_pc,quintil,quintil1,
         ess,
         # ess_inm,
         nation_t1,
         know_inm,
         know_inm_bi,
         know_inm_t1t4,
         frien_inm,
         frien_inm_bi,
         frien_inm_t1t4,
         pos_id,
         edad)  %>% 
  filter(muestra == 1) #keep original sample (vs refresh)

# sjmisc::frq(df_study1$ola)
sjPlot::tab_xtab(df_study1$muestra,df_study1$ola)

df_study1_2 <- 
elsoc_long_2016_2021 %>% 
  select(idencuesta,ola,region,region_cod,comuna,comuna_cod,
         muestra,
         cuestion_mig,
         starts_with("in_"),
         educ,
         educ_n,
         ing_pc,
         quintil,
         quintil1,
         ess,
         nation_t1,
         know_inm_t1t4,
         frien_inm_t1t4,
         pos_id,
         edad
         ) %>% 
  filter(muestra == 1) %>% #keep original sample (vs refresh)
  na.omit()

sjPlot::view_df(df_study1_2,show.frq = T,show.values = T,show.na = T,show.prc = T)
sjPlot::tab_xtab(var.row = df_study1_2$muestra,
                 var.col = df_study1_2$ola)

# sjmisc::frq(df_study1_2$ola)
# sjmisc::frq(df_study1_2$muestra)
# sjmisc::frq(df_study1_2$cuestion_mig)
# sjmisc::frq(df_study1_2$idencuesta,show.na = F) %>% data.frame() %>% View()

# Dataset fixed at t5_________________________________________________________
# keep idencuesta for the t5
id <- distinct(df_study1_2 %>% select(idencuesta,ola) %>% filter(ola==5))
# filter data by the idencuesta of t5
df_study1_3 <- 
  df_study1_2 %>%  filter(idencuesta %in% id$idencuesta)

# sjmisc::frq(df_study1_2$comuna)
# sjPlot::view_df(df_study1_3,show.frq = T,show.values = T,show.na = T,show.prc = T)
# 
# sjPlot::tab_xtab(var.row = df_study1_3$cuestion_mig,
#                  var.col = df_study1_3$ola)
# 
# sjPlot::tab_xtab(var.row = df_study1_3$muestra,
#                  var.col = df_study1_3$ola)

# sjPlot::view_df(df_study1,show.frq = T,show.values = T,show.na = T)

# SAVE DATA____________________________________________________________________
save(df_study1,file = here::here("input/data-proc/study_1.RData"))
save(df_study1_2,file = here::here("input/data-proc/study_1_2.RData"))
save(df_study1_3,file = here::here("input/data-proc/study_1_3.RData"))

# # save codebook
sjPlot::view_df(df_study1,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1.html"))

sjPlot::view_df(df_study1_2,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1_2.html"))

sjPlot::view_df(df_study1_3,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1_3.html"))
```

@@

# Select and organize variables________________________________________________
df_study1_comunas <- 
df_f %>%
  mutate(comuna=sjlabelled::as_character(comuna_cod)) %>% 
  dplyr::select(comuna,
                comuna_cod,
                inm_prop_cas17_w=inm_2017_cas_w,
                inm_tota_cen17=inm_totcenso17,
                inm_prop_cen17=inm_propcenso17,
                inm_tota_cit17=inm_cit17,
                inm_prop_citproy17=inm_cit_proye17,
                inm_prop_demproy18=inm_dem_proye18,
                inm_prop_demproy19=inm_dem_proye19,
                inm_prop_demproy20=inm_dem_proye20,
                inm_prop_cas20_w=inm_2020_cas_w) %>% 
  mutate(dif_inm = inm_prop_cas20_w-inm_prop_cas17_w)
df_study1_comunas$comuna_lc <- NULL
# names(df_study1_comunas)

@@

load(file = here::here("input/data-proc/study_1.RData"))
load(file = here::here("input/data-proc/study_1_2.RData"))
load(file = here::here("input/data-proc/study_1_3.RData"))
load(file = here::here("input/data-proc/study_1_comunas.RData"))

df_study1_ind_comunas <- 
 dplyr::left_join(x = df_study1,
                  y = df_study1_comunas, 
                  by = "comuna_cod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

df_study1_2_ind_comunas <- 
 dplyr::left_join(x = df_study1_2,
                  y = df_study1_comunas, 
                  by = "comuna_cod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

df_study1_3_ind_comunas <- 
 dplyr::left_join(x = df_study1_3,
                  y = df_study1_comunas, 
                  by = "comuna_cod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

# save data____________________________________________________________________
save(df_study1_ind_comunas,
     file = here::here("input/data-proc/df_study1_ind_comunas.RData"))
save(df_study1_2_ind_comunas,
     file = here::here("input/data-proc/df_study1_2_ind_comunas.RData"))
save(df_study1_3_ind_comunas,
     file = here::here("input/data-proc/df_study1_3_ind_comunas.RData"))

# save codebook
sjPlot::view_df(df_study1_ind_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_ind_comunas.html"))

sjPlot::view_df(df_study1_2_ind_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_2_ind_comunas.html"))

sjPlot::view_df(df_study1_3_ind_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_3_ind_comunas.html"))
```

>>>>

#Recoding of education to years based on casen 2017.
elsoc_long_2016_2021$educyear<- as.numeric(
  car::recode(elsoc_long_2016_2021$m01, 
              "1=0;2=4.3;3=7.5;4=9.8;5=12.02;6=13.9;
               7=14.8;8=14.9;9=16.9;10=19.07;c(-888,-999)=NA", 
              as.numeric = T))

elsoc_long_2016_2021$educyear <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$educyear,
                      label = "Education in years")

class(elsoc_long_2016_2021$educyear)
sjmisc::frq(elsoc_long_2016_2021$educyear)

@@

elsoc_long_2016_2021$nation <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$nation, 
                      label = "Nationality") 
elsoc_long_2016_2021$nation <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$nation,
                       labels = c("Chilean","Peruvian","Argentina","Colombian",
                                  "Bolivian", "Haitian","Spanish","Other"))

sjmisc::frq(elsoc_long_2016_2021$nation)

@@

elsoc_long_2016_2021$pos_id <- factor(elsoc_long_2016_2021$pos_id,
                                      levels = levels(elsoc_long_2016_2021$pos_id))

@@

table(elsoc$nation==elsoc$nation_t1)
sjmisc::frq(elsoc$nation_t1)

elsoc$nation <- NULL; elsoc$nation_fix <- NULL; elsoc$check_nation <- NULL

elsoc$nation_t1 <- set_label(elsoc$nation_t1, label = "Nationality")
elsoc$nation_t1 <- set_labels(elsoc$nation_t1,
                              labels =c("Chilean","Peruvian",
                                        "Argentina","Colombian",
                                        "Bolivian", "Haitian","Spanish","Other"))
elsoc$nation_t1 <- factor(elsoc$nation_t1,
                          levels = 1:8,
                          labels = c("Chilean","Peruvian",
                                     "Argentina","Colombian",
                                     "Bolivian", "Haitian","Spanish","Other"))
sjmisc::frq(elsoc$nation_t1)
# KNOW inmigrants _____________________________
sjPlot::tab_xtab(elsoc$know_inm,
                 elsoc$ola,show.cell.prc = T,show.na = T)
sjmisc::frq(elsoc$know_inm)
elsoc$know_inm_bi <- car::recode(elsoc$know_inm,
                                                "1=0;2:5=1")
sjmisc::frq(elsoc$know_inm_bi)

know_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(know_inm_bi_t4=know_inm_bi[ola==4],
            know_inm_bi_t1=know_inm_bi[ola==1],
            know_inm_t1t4 = know_inm_bi[ola==4] - know_inm_bi[ola==1]
            )

elsoc <- left_join(x = elsoc,y = know_inm_bi, by = "idencuesta")
sjmisc::frq(elsoc$know_inm_t1t4)
elsoc$know_inm_t1t4 <- set_label(elsoc$know_inm_t1t4,
                                  label = "Know immigrants (diff. t4 - t1)")
# sjmisc::frq(elsoc$know_inm_t1t4)
# sjPlot::tab_xtab(elsoc$know_inm_t1t4,elsoc$ola)

@@

frien_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(frien_inm_bi_t4=frien_inm_bi[ola==4],
            frien_inm_bi_t1=frien_inm_bi[ola==1],
            frien_inm_t1t4 = frien_inm_bi[ola==4] - frien_inm_bi[ola==1]
            )

elsoc <- left_join(x = elsoc,y = frien_inm_bi, by = "idencuesta")
summary(elsoc$frien_inm_t1t4)
# if NA in difference, impute data from t4
elsoc$frien_inm_t1t4 <- if_else(condition = is.na(elsoc$frien_inm_t1t4),
                                true = elsoc$frien_inm_bi_t4,
                                false = elsoc$frien_inm_t1t4 )
summary(elsoc$frien_inm_t1t4)
# if NA in difference, impute data from t1
elsoc$frien_inm_t1t4 <- if_else(condition = is.na(elsoc$frien_inm_t1t4),
                                true = elsoc$frien_inm_bi_t1,
                                false = elsoc$frien_inm_t1t4)
summary(elsoc$frien_inm_t1t4)

elsoc$frien_inm_t1t4 <- 
  set_label(elsoc$frien_inm_t1t4,
            label = "Have immigrant friends (diff. t4 - t1)")

sjmisc::frq(elsoc$frien_inm_t1t4)
# sjPlot::tab_xtab(elsoc$frien_inm_t1t4,elsoc$ola)

@@

df_study1 <- 
elsoc_long_2016_2021 %>% 
  filter(muestra == 1) %>% #keep original sample (vs refresh)
  select(idencuesta,ola,region,region_cod,comuna,comunacod=comuna_cod,
         muestra,
         cuestion_mig,
         starts_with("in_"),
         educ,educyear,
         # ing_pc,
         # quintil,
         quintil1,
         ess,
         # ess_inm,
         nation_t1,
         # know_inm,
         # know_inm_bi,
         # frien_inm_bi_t4,
         # frien_inm_bi_t1,
         know_inm_t1t4,
         # frien_inm,
         # frien_inm_bi,
         frien_inm_t1t4,
         pos_id,
         edad)

# Reshape long to wide
df_study1_wide <- df_study1 %>% 
  tidyr::pivot_wider(id_cols = c("idencuesta","muestra"),
                     names_from = "ola",
                     # names_prefix = c("educ","educyear","ing_pc","quintil","quintil1"),
                     values_from = names(select(df_study1,comuna,comunacod,cuestion_mig,in_simpat:edad))
                     )

# fix data to w01 values
df_study1_wide$edad_2 <-df_study1_wide$edad_1 #age
df_study1_wide$edad_3 <-df_study1_wide$edad_1
df_study1_wide$edad_4 <-df_study1_wide$edad_1
df_study1_wide$edad_5 <-df_study1_wide$edad_1

df_study1_wide$educ_2 <-df_study1_wide$educ_1 #education
df_study1_wide$educ_3 <-df_study1_wide$educ_1
df_study1_wide$educ_4 <-df_study1_wide$educ_1
df_study1_wide$educ_5 <-df_study1_wide$educ_1

df_study1_wide$educyear_2 <-df_study1_wide$educyear_1 #education years
df_study1_wide$educyear_3 <-df_study1_wide$educyear_1
df_study1_wide$educyear_4 <-df_study1_wide$educyear_1
df_study1_wide$educyear_5 <-df_study1_wide$educyear_1

df_study1_wide$quintil1_2 <-df_study1_wide$quintil1_1 #quintiles
df_study1_wide$quintil1_3 <-df_study1_wide$quintil1_1
df_study1_wide$quintil1_4 <-df_study1_wide$quintil1_1
df_study1_wide$quintil1_5 <-df_study1_wide$quintil1_1

df_study1_wide$ess_2 <-df_study1_wide$ess_1 # subjective status
df_study1_wide$ess_3 <-df_study1_wide$ess_1
df_study1_wide$ess_4 <-df_study1_wide$ess_1
df_study1_wide$ess_5 <-df_study1_wide$ess_1

df_study1_wide$pos_id_2 <-df_study1_wide$pos_id_1 # political position
df_study1_wide$pos_id_3 <-df_study1_wide$pos_id_1
df_study1_wide$pos_id_4 <-df_study1_wide$pos_id_1
df_study1_wide$pos_id_5 <-df_study1_wide$pos_id_1

df_study1_wide$nation_t1_2 <-df_study1_wide$nation_t1_1 # nation
df_study1_wide$nation_t1_3 <-df_study1_wide$nation_t1_1
df_study1_wide$nation_t1_4 <-df_study1_wide$nation_t1_1
df_study1_wide$nation_t1_5 <-df_study1_wide$nation_t1_1

df_study1_wide$know_inm_t1t4_2 <-df_study1_wide$know_inm_t1t4_1 # know immigrants
df_study1_wide$know_inm_t1t4_3 <-df_study1_wide$know_inm_t1t4_1
df_study1_wide$know_inm_t1t4_4 <-df_study1_wide$know_inm_t1t4_1
df_study1_wide$know_inm_t1t4_5 <-df_study1_wide$know_inm_t1t4_1

df_study1_wide$frien_inm_t1t4_2 <- df_study1_wide$frien_inm_t1t4_1 # immigrant friends
df_study1_wide$frien_inm_t1t4_3 <- df_study1_wide$frien_inm_t1t4_1
df_study1_wide$frien_inm_t1t4_4 <- df_study1_wide$frien_inm_t1t4_1
df_study1_wide$frien_inm_t1t4_5 <- df_study1_wide$frien_inm_t1t4_1

df_study1_wide$comuna_2 <-df_study1_wide$comuna_1 #comuna
df_study1_wide$comuna_3 <-df_study1_wide$comuna_1
df_study1_wide$comuna_4 <-df_study1_wide$comuna_1
df_study1_wide$comuna_5 <-df_study1_wide$comuna_1

df_study1_wide$comunacod_2 <-df_study1_wide$comunacod_1 #comuna
df_study1_wide$comunacod_3 <-df_study1_wide$comunacod_1
df_study1_wide$comunacod_4 <-df_study1_wide$comunacod_1
df_study1_wide$comunacod_5 <-df_study1_wide$comunacod_1

dim(df_study1_wide)

sjPlot::view_df(df_study1_wide,
                show.frq = T,show.values = T,show.na = T,show.prc = T, show.type = T)

# reshape from long to wide
pacman::p_load(datasets,data.table)
df_study1_long <- data.table::melt.data.table(data.table::setDT(df_study1_wide),
              id.vars = c("idencuesta","muestra"),
              variable.name = c("ola"),
              measure = patterns("^comuna_","^comunacod_","^cuestion_mig_",
                                 "^in_simpat_","^in_simili_","^in_ansied_","^in_valfam_",
                                 "^in_valami_","^in_amsimb_","^in_amreal_","^in_acpier_",
                                 "^in_acadop_","^in_amigcl_",
                                 "^educ_","^educyear_","^quintil1_","^ess_","^nation_t1_",
                                 "^know_inm_t1t4_","^frien_inm_t1t4_","^pos_id_",
                                 "^edad_"
                                 ),
              value.name = c("comuna","comunacod","cuestion_mig",
                             "in_simpat","in_simili","in_ansied","in_valfam",
                             "in_valami","in_amsimb","in_amreal",
                             "in_acpier","in_acadop","in_amigcl",
                             "educ","educyear","quintil1","ess","nation_t1",
                             "know_inm_t1t4","frien_inm_t1t4","pos_id",
                             "edad"),
              na.rm = F,value.factor = TRUE
              )

names(df_study1_long) #check names of long dataset
dim(df_study1_long) #check dimensions of the dataframe
# filter the sataset for the waves 1 to 5
df_study1_long <-
df_study1_long %>% 
  filter(ola %in% c(1,2,3,4,5)) %>% 
  mutate(ola=factor(ola,levels = 1:5,labels = 1:5))
dim(df_study1_long) #check, now is OK

df_study1_long <- 
set_label(x = df_study1_long,
          label = get_label(select(df_study1,names(df_study1_long))))

sjPlot::view_df(df_study1_long,
                show.frq = T,show.values = T,show.na = T,show.prc = T,
                show.type = T)
#______________________________________________________________________________
# obtain the idencuesta for wave 5
ids <- 
  df_study1 %>% 
  select(idencuesta,ola) %>% 
  filter(ola==5) %>% 
  sjmisc::frq(idencuesta,show.na = F) %>% as.data.frame()

# filter data by the idencuesta of t5
df_study1_long_t5 <- 
  df_study1_long %>%
  filter(idencuesta %in% ids$val)

names(df_study1_long_t5)
dim(df_study1_long_t5)
sjmisc::frq(df_study1_long_t5$ola)

# SAVE DATA____________________________________________________________________
save(df_study1_long,file = here::here("input/data-proc/df_study1_long.RData"))
save(df_study1_long_t5,file = here::here("input/data-proc/df_study1_long_t5.RData"))

# save codebook
sjPlot::view_df(df_study1_long,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1_long.html"))

sjPlot::view_df(df_study1_long_t5,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1_long_t5.html"))
```

@@

# Select and organize variables________________________________________________
df_study1_comunas <- 
df_f %>%
  mutate(comuna=sjlabelled::as_character(comuna_cod)) %>% 
  dplyr::select(comuna,
                comunacod=comuna_cod,
                inm_prop_cas17_w=inm_2017_cas_w,
                inm_tota_cen17=inm_totcenso17,
                inm_prop_cen17=inm_propcenso17,
                inm_tota_cit17=inm_cit17,
                inm_prop_citproy17=inm_cit_proye17,
                inm_prop_demproy18=inm_dem_proye18,
                inm_prop_demproy19=inm_dem_proye19,
                inm_prop_demproy20=inm_dem_proye20,
                inm_prop_cas20_w=inm_2020_cas_w) %>% 
  mutate(dif_inm = inm_prop_cas20_w-inm_prop_cas17_w)
df_study1_comunas$comuna_lc <- NULL
# names(df_study1_comunas)

@@

load(file = here::here("input/data-proc/df_study1_long.RData"))
load(file = here::here("input/data-proc/df_study1_long_t5.RData"))
load(file = here::here("input/data-proc/study_1_comunas.RData"))

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

df_study_long_t5_comunas <- 
 dplyr::left_join(x = df_study1_long_t5,
                  y = df_study1_comunas, 
                  by = "comunacod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

# save data____________________________________________________________________
save(df_study1_long_comunas,
     file = here::here("input/data-proc/df_study1_long_comunas.RData"))
save(df_study_long_t5_comunas,
     file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# save codebook
sjPlot::view_df(df_study1_long_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_long_comunas.html"))

sjPlot::view_df(df_study_long_t5_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study_long_t5_comunas.html"))
```
